---
title: Parsons problems
author: Andrie de Vries
date: "`r Sys.Date()`"
output: learnr::tutorial
runtime: shiny_prerendered
---



```{r setup, include=FALSE}
library(learnr)
library(parsons)
library(magrittr)
```


## Hello world!

A Parsons problem gives the student some programming statements in random order.  The student then constructs an answer by dragging the statements into the correct order.

Here is an example.  Drag the statements from the top panel to the bottom panel to produce "Hello World!".

```{r Hello-world, echo=FALSE}
question_parsons(
  initial = c(
    "Hello",
    "World",
    "!"
  ),
  pass_if(
    c(
    "Hello",
    "World",
    "!"
    )
  )
)
```


## Constructing a parsons's problem

To create a parsons problem in a `learnr` tutorial, use the `question_parson()` function.

You must provide at minimum:

* The `initial` set of values, as a character vector

* A "correct" answer

Note that, when using only this minimal specification, the only feedback the student will ever get is "Incorrect, try again".

```{r explain-1}
question_parsons(
  initial = c(
    "Hello",
    "World",
    "!"
  ),
  answer(
    c(
    "Hello",
    "World",
    "!"
    ),
    correct = TRUE
  )
)
```


## Using pass and fail conditions

An alternative way to specify the correct answer(s) is to supply a `pass_if()` statement.  Using `pass_if()` and `fail_if()` is a powerful way to provide feedback to your students.

These `pass_if()` and `fail_if()` statements are evaluated in turn, until the first expectation evaluates to `TRUE`, and the `leanr` will provide the feedback in the `message`.

You can specify `pass_if()` as well as `fail_if()` in any of the following ways:

* A character vector, that must be matched exactly, or

* A function in the tradition form `function(x) ...`, e.g. `function(x) length(x) < 3`

* A function specified using the `rlang` tidy evaluation formula notation, e.g. `~length(.) < 3`


This next example will give feedback if the length of the answer is 2 or fewer items.

```{r explain-2}
question_parsons(
  initial = c(
    "Hello",
    "World",
    "!"
  ),
  pass_if(
    c(
    "Hello",
    "World",
    "!"
    )
  ),
  fail_if(
    ~length(.) <= 2,
    "Provide more answers"
  )
)
```




## Using multiple conditions

Create a statement that uses `iris` data, then does some mutation and finally creates a summary.

```{r iris}
question_parsons(
  initial = c(
    "iris",
    "mutate(...)",
    "summarize(...)",
    "print()"
  ),
  pass_if(
    c(
      "iris",
      "mutate(...)",
      "summarize(...)"
    )
  ),
  fail_if(
    ~length(.) < 2,
    message = "Include at least two answers"
  ),
  fail_if(
    function(x){"print()" %in% x},
    message = "You should not include print() in your answer"
  ),
  fail_if(
    ~{.[1] != "iris"},
    message = "Your solution should start with 'iris'"
  )
)
```



